\sysfull

### 2018-08-05 paper/asplos19/paging.tex
partial commit

% \textcolor{red}{[additional motivation for coala memory virtualization] we should emphasize that Coala programming model removes the burden of identifying the write-after-read dependencies from the programmer  as compared to Chain. And it does not require a specific compiler that cannot consider a runtime dependent behavior like Interrupts service handling to guarantee memory protection, as in Alpaca.}
%
\sys's {\em virtual memory manager} exposes non-volatile memory for
\emph{protected} variables to the application as a virtual address space
partitioned into privatized pages, a technique we call \emph{dynamic pages privatization}.
%
A program's tasks read and write these protected variables, using them like any
other data in the program.
%
The virtual memory manager automatically privatize the pages associated with the accessed protected variables.
%
When a task completes, the virtual memory manager ensures that updated pages
are committed to main memory and visible to subesequently executed tasks.
%
If the power interrupts a task, the virtual memory manager ensures that
the task sees consistent memory state when it restarts its execution.
%
The virtual memory manager ensures consistency even if a task or a sequence of tasks include WAR dependences that could compromise consistency~\cite{ratchet,dino}.

\sys's virtual memory manager \sys abstracts non-volatile storage (e.g.,
variables in FRAM) from tasks.

@@

Protected variables remain consistent and are durable across power failures.

@@

While ensuring variables remain durable, \sys avoids accessing non-volatile
memory when possible, by copying pages of data into a {\em working memory} in the device's SRAM, which
has a lower latency and energy cost to access than the device's FRAM (as we
showed in Section~\ref{sec:background}).
On a commit, \sys atomically copies all updated (i.e., ``dirty'') pages from their
space in the working memory back into their location in the non-volatile
memory.

@@

\sys moves pages of data efficiently using hardware accelerated Direct Memory

@@

\texttt{\underline{store}} (underlined locations are non-volatile).  When a
task accesses a page, the memory manager swaps the page from its home location

@@

\sys uses a two-phase commit to write dirty pages from the \texttt{working}
buffer back to their home location in \texttt{\underline{store}} atomically,
ensuring data consistency even in the presence of a power failure during commit.

@@

page buffer. Later, to commit the page, \sys writes it from its
\texttt{\underline{shadow}} location back to its home location in
\texttt{\underline{store}}.

>>>>

% \textcolor{red}{[additional motivation for coala memory virtualization] we should emphasize that Coala programming model removes the burden of identifying the write-after-read dependencies from the programmer  as compared to Chain. And it does not require a specific compiler that cannot consider a runtime dependent behavior like Interrupts service handling to guarantee memory protection, as in Alpaca.}

@@

\sys's {\em virtual memory manager} (VMM) abstracts the physical address space of the non-volatile memory (FRAM) and divides it into \emph{private} and \emph{shadow} buffers. Each buffer is divided into pages. The VMM prohibits applications from directly access these buffers. Instead, it redirects any data request to the \emph{working} buffer which is located in the volatile memory (SRAM) has a lower latency and energy cost to access than the device's FRAM. It populates working buffer with the privatized pages from non-volatile memory. When a coalesced task completes, the VMM ensures that updated pages are committed to main memory and visible to subsequently executed tasks. If the power interrupts a task, the VMM ensures that the task sees consistent memory state when it restarts its execution. The VMM ensures consistency even if a task or a sequence of tasks include WAR dependences that could compromise consistency~\cite{ratchet,dino}.

@@

On a commit, the VMM atomically copies all ``dirty'' pages back into their location in the non-volatile memory.

@@

the VMM moves pages of data efficiently using hardware accelerated Direct Memory

@@

\texttt{\underline{private}} (underlined locations are non-volatile).  When a
task accesses a page, the VMM swaps the page from its home location

@@

The VMM utilizes a two-phase commit to write dirty pages from the \texttt{working}
buffer back to their home location in \texttt{\underline{private}}. It optimizes this process by using an indirection table to abstract the location of the \texttt{\underline{private}} buffer and
to eliminate the need for the second page copy.

@@

page buffer. \\
